Topological Analysis of Bitcoin's Lightning Network

### 2019-01-15 article/main.tex
Fixing abstract and conclusion by Dani

\begin{abstract}
Bitcoin's Lightning Network (LN) is a scalability solution for Bitcoin, which allows transactions to be issued with negligible fees and settle transactions instantly at scale. In order to use LN, funds need to be locked in payment channels on the Bitcoin blockchain (Layer-1), that one may use them in LN (Layer-2). LN is comprised of many payment channels forming a payment channel network. LN's promise is that a few payment channels already enable anyone to efficiently, securely and privately route payments across the whole network. In this paper we quantify the structural properties of LN and argue that LN's current topological properties could have been ameliorated in order to enable LN to reach its true potential.  
\end{abstract}
\keywords{Bitcoin, Lightning Network, Network Topology, Payment Channel Network}

@@

LN gradually increased adoption and attraction throughout 2018, which resulted in 3 independent client implementations (c-lightning, eclair and lnd) and \num[group-separator={,}]{2344} nodes joining LN as of 2019, January 3rd. The density of a graph is defined as $D=\frac{2\mid E\mid}{\mid V\mid \mid V-1\mid}$  which is the ratio of present and potential edges. As it is shown in Figure \ref{fig:properties}. LN is quite a parse graph. This is further justified by the fact that LN has \num[group-separator={,}]{530} bridges, edges which deletion increases the number of connected components. Although LN is consisted of $2$ components, the second component has only $3$ nodes. The low transitivity, fraction of present and possible triangles in the graph, highlights the sparseness of LN as well.

\begin{wrapfigure}{r}{0.6\textwidth}
	\caption{LN's degree distribution}\label{fig:degreedist}
	\begin{center}
		\includegraphics[width=0.85\textwidth]{degreehistogramlogscale.png}
	\end{center}	
\end{wrapfigure}

@@

\subsection{Scale-freeness of LN}

@@

\section{Conclusion}
In summary, a better understanding of the network topology is essential
to improve the robustness of complex systems, like LN. Network resilience depends on topology. LN is well approximated by the scale-free model and also its attack tolerance properties are similar to that of scale-free networks; namely, LN is robust against random failures, however it is quite vulnerable against targeted attacks. 
Shiny figures of LN's topology, like Figure~\ref{fig:lntopology}, convey only false sense of security and robustness, therefore to provide robust Layer 2 solutions for blockchains, the community needs to aim at building resilient network topologies.
\section{Acknowledgements}
We are grateful for the insightful comments and discussions to Chris Buckland, Olaoluwa Osuntokun and Alex Bosworth.

>>>>

\begin{abstract}
Bitcoin's Lightning Network (LN) is a scalability solution for Bitcoin allowing transactions to be issued with negligible fees and settled instantly at scale. In order to use LN, funds need to be locked in payment channels on the Bitcoin blockchain (Layer-1) for subsequent use in LN (Layer-2). LN is comprised of many payment channels forming a payment channel network. LN's promise is that relatively few payment channels already enable anyone to efficiently, securely and privately route payments across the whole network. In this paper, we quantify the structural properties of LN and argue that LN's current topological properties can be ameliorated in order to improve the security of LN, enabling it to reach its true potential.  
\end{abstract}
\keywords{Bitcoin, Lightning Network, Network Security, Network Topology, Payment Channel Network, Network Robustness}

@@

LN gradually increased adoption and attraction throughout 2018, which resulted in 3 independent client implementations (c-lightning\footnote{https://github.com/ElementsProject/lightning/}, eclair\footnote{https://github.com/ACINQ/eclair} and lnd\footnote{https://github.com/lightningnetwork/lnd}) and \num[group-separator={,}]{2344} nodes joining LN as of 2019, January 3rd. The density of a graph is defined as $D=\frac{2\mid E\mid}{\mid V\mid \mid V-1\mid}$  which is the ratio of present and potential edges. As it is shown in Figure \ref{fig:properties}. LN is quite a parse graph. This is further justified by the fact that LN has \num[group-separator={,}]{530} bridges, edges which deletion increases the number of connected components. Although LN is consisted of $2$ components, the second component has only $3$ nodes. The low transitivity, fraction of present and possible triangles in the graph, highlights the sparseness of LN as well.

\begin{wrapfigure}{r}{0.6\textwidth}
	\caption{LN's degree distribution}\label{fig:degreedist}
	\begin{center}
		\includegraphics[width=0.85\textwidth]{degreehistogramloglogscale.png}
	\end{center}	
\end{wrapfigure}

@@

\subsection{Analysis of LN's degree distribution}

@@

\section{Conclusion}
In summary, a better understanding of the network topology is essential
for improving the robustness of complex systems, like LN. Networks' resilience depends on their topology. LN is well approximated by the scale-free model and also its attack tolerance properties are similar to those of scale-free networks; in particular, while LN is robust against random failures, it is quite vulnerable in the face of targeted attacks. 
High-level depictions of LN's topology, like Figure~\ref{fig:lntopology}, convey a false image of security and robustness. As we have demonstrated, LN is structurally weak against rational adversaries. Thus, to provide robust Layer 2 solutions for blockchains, such as LN and Raiden, the community needs to aim at building resilient network topologies.
\section{Acknowledgements}
We are grateful for the insightful comments and discussions to Chris Buckland, Olaoluwa Osuntokun and Alex Bosworth.
